Things To Do With Calc:

%%1. Second Derivatives in Implicit Diff
%%2. Normal lines throughout
%%3. Jen's remarks
4. Stress horizontal tangent lines in deriv chapters
%%5. Fix continuity/interval stuff
%%6. Inverse functions - composition = x, finding, etc2
7. Compare newtons method to bisection method, exact example
%%8. Front cover material
9. Add questions about position, what's velocity, in derivative section
10. Is it clear why we have signed area? Both -delta x and -height issues.
11. Work on integrating speed/velocity to get distance traveled/displacement.
12. Add difference quotient problems to 1.3 (barely in text)
13. 1.6 discussion on indeterminate forms is confusing.
14. Check epsilon/delta proofs in 1.2. Does the text match my own teaching method?
15. Add questions to 1.3 like $\lim_{x\to9}\frac{\sqrt{x}-3}{x-9}$
16. Theorem: Area between curves. Renumber around it?
17. Section 2.2, put equation numbers with the approximation/tangent line stuff
%**18. Add normal line stuff
%**19. Logarithmic differentiation
%**20. 3.1 HW does not have any Find Extreme Values on Interval problems!!
21. Add plots of functions to Trig Integrals section to show periodicity, etc.
%22. Add to Hyperbolic stuff with integration - skip the $tanh^{-1}x$ stuff and use $\ln $ stuff instead.
23. Give plot of f', ask about f and f''
24. Fix critical point issue where f(c) does not exist
25. Add surfaces of revolution to Section 10.1
%26. Fix parallel vector definitions (add to cross product)
27. Add Even/Odd functions to integration sections

28. Add graphical limit stuff to 1.4.
29. Add better related rates? Inverted cone like in summer '14 exam?

